---
title: "Lab 5"
author: "Cristina Robinson"
date: "10/25/2021"
output: 
  html_document: 
    theme: united
    toc: yes
    code_folding: hide
---

```{r setup, include = TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(effsize)
```

# Part 1: Confidence intervals 

In this section, we'll use the 't.test()' function to calculate confidence intervals. 

### Example 1

Create a single mock sample containing a number of values, then learn to use 't.test()' to return confidence intervals, and learn about in-line code referencing so our text becomes more reproducible, too. 

```{r}
# Create a mock sample
otter_lengths <- c(30, 45, 28, 31, 34, 46, 52, 29, 90, 72, 112)

# Find the confidence level: 
otter_ci <-t.test(otter_lengths)

# Find the standard deviation
otter_sd <- (otter_lengths)
```
# What does confidence interval actually mean? 

# This means if we took multiple samples form this population and calculated a CI for each of them, we would expect that 95% of the CI calculated would contain the true mean.

Mean otter length is 36.9 inches $\pm$ 9.3 (mean $\pm$ sd, n =8) with a 95% confidence interval of [29.1, 44.7] inches. 

#### Now, using in-line referencing

Mean otter length is `r round(otter_ci$estimate, 1)` inches with a 95% confidence interval of [`r round(otter_ci$conf.int[1], 1)`, `r round(otter_ci$conf.int[2], 1)`] inches. 

## Part 2: Two-sample t-tests

### Example 1

Make two mock samples, and ask the question: do we have sufficient evidence to make us reject the null hupothesis that these sample were drawn from populations with the same mean?

```{r}
# Make my mock samples
oak_trees <- c(20, 19, 24, 28, 34, 12, 15, 25, 200, 180, 300)

pine_trees <- c(39, 26, 20, 30, 37, 22, 19, 18)

# Two-sample t-test
trees_t <- t.test(oak_trees, pine_trees)

# Null hypothesis: mean heights are the same
# ie.: Trees are drawn from populations with the same mean height 

```
If these samples were drawn from populations with the same mean heights, [start with null hypothesis] then there is a 28.7% chance that taking a random sample from each population and finding that the population means are the same from random chance. 
Not enough evidence to reject the null hypothesis. 

Allison wrote: The mean heights of oak and pine trees were (X +- Y and ( X +- Y), respectively, and the difference was not significant (t(`r trees_t$parameter`) = `r trees_t$statistic`, p = `r trees_t$p.value`)

"two-sample t-test; t(df) = t-statistic, p = p-value"  

*AVOID*: p = 0

When things get really small (usually p < 0.001)

*Not great*: p = 0.00000000013
*Better*: p < 0.001 

## Part 3: Another t-test with cars data

Using `mpg` data

### Take a look at the data
```{r}
compact_suv <- mpg %>%
  filter(class %in% c("compact", "suv"))
# Check for remaining levels by using the unique function 
unique(compact_suv$class)
```

Create a histogram of city gas mileage (city) faceted by class starting from compact_suv.

```{r}
ggplot(data = compact_suv, aes(x = cty)) +
  geom_histogram(bins =10) +
  facet_wrap(~ class)

ggplot(data = compact_suv, aes(sample = cty)) +
  geom_qq() +
  facet_wrap(~ class)

```

Find some summary statistics for each group

```{r}
car_stats <- compact_suv %>%
  group_by(class) %>%
  summarize(
    mean_city = round(mean(cty), 2),
    sd_city = sd(cty), 
    sample_size = n()
  )

car_stats
```

The t.test() function REALLY wants vectors of things. Use the `pull()` function to pull out a vector from a data frame. 

```{r}
compact_sample <- compact_suv %>%
  filter(class =="compact") %>%
  pull(cty)

# Your turn: do the same thing to get a vector of city gas mileage for SUVs

suv_sample <- compact_suv %>%
  filter(class == "suv") %>%
  pull(cty)

```

H0: Mean city gas mileages for SUVs and compact cars are the same

```{r}
t.test(compact_sample, suv_sample)
```
There is a significant difference in mean city gas mileage for SUVs and compact cars (t(df)) = t-statistic, (p < 0.001).

