---
title: "Lab 5"
author: "Cristina Robinson"
date: "10/25/2021"
output: 
  html_document: 
    theme: united
    toc: yes
    code_folding: hide
---

```{r setup, include = TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(effsize)
```

# Part 1: Confidence intervals 

In this section, we'll use the 't.test()' function to calculate confidence intervals. 

### Example 1

Create a single mock sample containing a number of values, then learn to use 't.test()' to return confidence intervals, and learn about in-line code referencing so our text becomes more reproducible, too. 

```{r}
# Create a mock sample
otter_lengths <- c(30, 45, 28, 31, 34, 46, 52, 29)

# Find the confidence level: 
otter_ci <-t.test(otter_lengths)

# Find the standard deviation
otter_sd <- (otter_lengths)
```
# What does confidence interval actually mean? 
## This means if we took multiple samples form this population and calculated a CI for each of them, we would expect that 95% of the CI calculated would contain the true mean.

Mean otter length is 36.9 inches $\pm$ 9.3 (mean $\pm$ sd, n =8) with a 95% confidence interval of [29.1, 44.7] inches. 

#### Now, using in-line referencing

Mean otter length is `r round(otter_ci$estimate, 1)` inches. 

